---
title: "Code-along, Week 08: Modelling pubs"
author: "Alex Homer"
date: "11 November 2021"
output: github_document
editor_options: 
  chunk_output_type: console
---

This week's data come from the UK's [Office for National Statistics](https://www.ons.gov.uk/).  We will be using the following datasets:

* [Public houses and bars by local authority](https://www.ons.gov.uk/businessindustryandtrade/business/activitysizeandlocation/datasets/publichousesandbarsbylocalauthority) (Copyright date: 2018)
* [Estimates of the population for the UK, England and Wales, Scotland and Northern Ireland ](https://www.ons.gov.uk/peoplepopulationandcommunity/populationandmigration/populationestimates/datasets/populationestimatesforukenglandandwalesscotlandandnorthernireland) (Copyright date: 2021)
* [Earnings and hours worked, place of residence by local authority: ASHE Table 8](https://www.ons.gov.uk/employmentandlabourmarket/peopleinwork/earningsandworkinghours/datasets/placeofresidencebylocalauthorityashetable8) (Copyright date: 2021)
* [Standard Area Measurements (2018) for Administrative Areas in the United Kingdom](https://geoportal.statistics.gov.uk/datasets/standard-area-measurements-2018-for-administrative-areas-in-the-united-kingdom/about) (Copyright date: 2019)
* [Life Expectancy by Local Authority](https://www.ons.gov.uk/datasets/life-expectancy-by-local-authority/editions/time-series/versions/1) (Copyright date: 2020)

The data are subject to crown copyright and database rights and are used under the [Open Government Licence v3.0](https://www.nationalarchives.gov.uk/doc/open-government-licence/version/3/).

```{r load-packages, message = FALSE}
library(tidyverse)
library(tidymodels)
library(here)
```

## Read data

I've already done some of the cleanup and joining in advance to save time in the live session.  You can see the cleanup script in the "data" folder of this repo.

```{r read-data, message = FALSE}
pubs_data <- readRDS(here("data/pubs-final.rds"))
```

The rest of this file will be filled in during the live session.